Viability of FTIR on fossil pollen

### 2020-12-03 manuscript.Rmd
dedicated packages file; function to extract sample depth from filename

```{r message=FALSE, warning=FALSE, include=FALSE}
library(here)
source(here("R","authors_and_affiliations.R"))
```

@@

as

@@

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}
library(here)
source(here("R","packages.R"))
source(here("R","authors_and_affiliations.R"))
```

@@

Abstract

@@

```{r}
count_grains = function(core){
  counts = core %>%
    group_by(type, depth, treatment) %>%
    summarise(count=n())
  return(counts)
}
count_grains(TSK)
```
